---
title: '7.8 Lab: Non-Linear Modeling'
author: "WangYong"
date: "2022/2/25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ISLR)
attach(Wage)
```
### 7.8.1 Polynomial Regression and Setup Functions
thogonal polynomials.
```{r}
fit <- lm(wage~poly(age, 4),data=Wage)
coef(summary(fit))
```
direct  (3种方式，自动、手工，cbind)
```{r}
fit2 <- lm(wage~poly(age,4,raw=T),data=Wage)
coef(summary(fit2))

fit2a <-lm(wage~age+I(age^2)+I(age^3)+I(age^4),data=Wage)
coef(fit2a)
fit2b=lm(wage~cbind(age ,age^2,age^3, age ^4),data=Wage)
coef(fit2b)
 
```

```{r}
agelims = range(age)
age.grid <- seq(from=agelims[1],to=agelims[2])
preds = predict(fit, newdata=list(age=age.grid),se=T)
se.bands = cbind(preds$fit + 2* preds$se.fit, preds$fit-2*preds$se.fit)
par(mfrow=c(1,2),mar=c(4.5,4.5,1,1),oma=c(0,0,4,0))
plot(age, wage, xlim=agelims, cex=.5, col='darkgrey')
title('Degress-4 Polynomial', outer=T)
lines(age.grid, preds$fit, lwd=2, col='blue')
matlines(age.grid, se.bands, lwd=1, col='blue',lty=3)

```
- compare the results of whether or not orthogonal set
note: the result is tini for our case.
```{r}
preds2 = predict(fit2, newdata=list(age=age.grid),se=T)
max(abs(preds$fit - preds2$fit))
```
- compare different polynomial level by anova
```{r}
fit.1=lm(wage~age ,data=Wage)
fit.2=lm(wage~poly(age ,2),data=Wage)
fit.3=lm(wage~poly(age ,3),data=Wage)
fit.4=lm(wage~poly(age ,4),data=Wage)
fit.5=lm(wage~poly(age ,5),data=Wage)
anova(fit.1,fit.2,fit.3,fit.4,fit.5)
```

By anova compare, we can find level3,or 4 is sufficient. level5 has no 
significant improve from Pvalue

The result is same when check coef from fit.5 directly. The pvalue is same as 
anova result. Note: level 5 include level 1,2,3,4 coefficients as well.

```{r}
coef(summary (fit.5))
# for example level to tvalue -11.983^2 is 154 which in anova test fit.2 F value
(-11.983)^2
```

- use anova to compare different type models
the models 3 is better when compare the pvalue
```{r}
fit.1=lm(wage~education +age ,data=Wage)
fit.2=lm(wage~education +poly(age ,2) ,data=Wage)
fit.3=lm(wage~education +poly(age ,3) ,data=Wage)
anova(fit.1,fit.2,fit.3)
```
## spline funtion
## GAM

