---
title: "6.5 Subset Selection Methods"
author: "WangYong"
date: "2022/2/24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ISLR)
library(leaps)
```

# 6.5.1 Best Subset Selection

Use hitters data
```{r}
print('Exploratory Dataset Hitters')
print('show predictors')
names(Hitters)
print('show dimensions' )
dim(Hitters)
print('Show NA value in Hitter$Salary variable')
table(is.na(Hitters$Salary))
```
remove salaray is NA rows.
```{r}
Hitters <- na.omit(Hitters)
dim(Hitters)
print('There is no NA salrary rows')
table(is.na(Hitters))
```
Using leaps library regsubsets function to find best variables
```{r}
library(leaps)
regfit.full = regsubsets(data=Hitters,Salary~.)
reg.summary<-summary(regfit.full)
reg.summary
reg.summary$rsq
```


plotting Rss, adjr2 and max point
```{r}
set.seed(1)
regfit.full = regsubsets(data=Hitters,Salary~.,nvmax=19)
reg.summary<-summary(regfit.full)
par(mfrow=c(1,2))
plot(reg.summary$rss,
     xlab='Number of Variables',
     ylab='RSS',
     type='l')
plot(reg.summary$adjr2,
     xlab="Number of Variables",
     ylab='Adjusted Rsq',
     type="l"
     )
max_point<- which.max(reg.summary$adjr2)
points (max_point,reg.summary$adjr2[11], col="red",cex=2,pch =20)
```

plot Cp, and BIC statistics and min point
```{r}
set.seed(1)
regfit.full = regsubsets(data=Hitters,Salary~.,nvmax=19)
reg.summary<-summary(regfit.full)
min_cp <- which.min(reg.summary$cp)
min_bic <- which.min(reg.summary$bic)
par(mfrow=c(1,2))
plot(reg.summary$cp,
     xlab='Number of Variables',
     ylab='Cp',
     type='l')
points (min_cp,reg.summary$cp[min_cp], col="red",cex=2,pch =20)
plot(reg.summary$bic,
     xlab="Number of Variables",
     ylab='BIC',
     type="l"
     )
points (min_bic,reg.summary$bic[min_bic],col="red",cex=2,pch =20)
```

Use regsubsets default plots
```{r}
plot(regfit.full, scale='r2')
plot(regfit.full, scale='adjr2')
plot(regfit.full, scale='Cp')
plot(regfit.full, scale='bic')
```

Get lowest BIC & related variables #6
according to above plot, we can get best performance variable.
in following way: 1.get id the the variable groups. 2. show the variable names

```{r}
# get lowest bic group id
best_bic_id <- which.min(reg.summary$bic)
# show coefficients
coef(regfit.full,6)
# show the variable names
names(coef(regfit.full,6))[-1]
```

# 6.5.2 step forward and back forward
NA

# 6.5.3Choosing Among Models Using the Validation Set
Approach and Cross-Validation
in order to get test error, we need train only in train observation
```{r}
set.seed(1)
nvmax <- 19
train <- sample(c(T,F),nrow(Hitters),replace = T)
test <-(!train)

regfit.best <- regsubsets(Salary~.,
                          data=Hitters[train,],
                          nvmax=nvmax)
test.mat <- model.matrix(Salary~., data=Hitters[test,])
val.errors =rep(NA ,nvmax)
for (i in seq(nvmax)){
  coefi = coef(regfit.best, id=i)
  pred = test.mat[,names(coefi)]%*% coefi
  val.errors[i] = mean((Hitters$Salary[test]-pred)^2)
}
val.errors
```

Finally train on full data and get best model
This time, 10 variable found is best group which is differnet than partial date.

```{r}
predict.regsubsets <- function(object,newdata, id){
 form <- as.formula(object$call[[2]])
 mat  <- model.matrix(form ,newdata)
 coefi<- coef(object, id=id)
 xvars<- names(coefi)
 mat[,xvars] %*% coefi
}

regfit.best <- regsubsets(Salary~.,data=Hitters, nvmax=nvmax)
coef(regfit.best, 10)
```
 
now let's cross validation by 10 folder
```{r}
k=10
set.seed(1)
folds = sample(1:k, nrow(Hitters),replace=T)
# cv.error is 10*19 matrix with NA value. it will be filled later
cv.errors = matrix(NA, k,19, dimnames=list(NULL, paste(1:nvmax)))
for ( j in seq(k)){
  best.fit <- regsubsets(Salary~.,
                         data=Hitters[folds!=j,],
                         nvmax=nvmax)
  for (i in seq(nvmax)){
    pred = predict(best.fit, Hitters[folds==j,],id=i)
    
    cv.errors[j,i]= mean((Hitters$Salary[folds==j]-pred)^2)
    
  }
} 

mean.cv.errors <-apply(cv.errors,2,mean)
mean.cv.errors

```

 plot the results
```{r}
par(mfrow=c(1,1))
plot(mean.cv.errors,type='b')
```
show the best group variables
```{r}
reg.best=regsubsets (Salary~.,data=Hitters , nvmax=19)
coef(reg.best,11)

```
